Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-17 introduction.tex
target -> potential
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1089 ccdd05d5-56c1-461a-bf98-85f6876523b4

The coalescence of compact binary systems consisting of neutron stars
 (\textsc{ns}) and/or black holes (\textsc{bh}) is presently the best
understood and most actively pursued target source of gravitational
radiation for ground-based gravitational-wave (\GW{}) detectors.
As a compact binary system loses energy to \GW{}s, its
orbital separation decays, leading to a runaway inspiral with the \GW{}
amplitude and frequency increasing until the system eventually merges.  It is
thought that if a \textsc{ns} is involved, it may become tidally disrupted near
the merger and fuel a bright electromagnetic (\EM{})
counterpart~\citep{shibata:2007}. Observation of an \EM{} counterpart to a
candidate \GW{} event will vastly boost confidence in the \GW{} detection and
will often provide sufficient sky localization to determine
the source's host galaxy and therefore measure the source's redshift. The
\GW{} observation of this event will also provide a luminosity
distance measurement. With both quantities, we can
immediately measure the Hubble constant with unprecedented
accuracy and without systematics dependent on the standard cosmic distance
ladder~\citep{2010ApJ...725..496N}. The most efficient means of obtaining
such joint observations is through the rapid identification and dissemination
of candidate \GW{} events.

>>>>

The coalescence of compact binary systems consisting of neutron stars
 (\textsc{ns}) and/or black holes (\textsc{bh}) is presently the best
understood and most actively pursued potential source of gravitational
radiation for ground-based gravitational-wave (\GW{}) detectors.
As a compact binary system loses energy to \GW{}s, its
orbital separation decays, leading to a runaway inspiral with the \GW{}
amplitude and frequency increasing until the system eventually merges.  It is
thought that if a \textsc{ns} is involved, it may become tidally disrupted near
the merger and fuel a bright electromagnetic (\EM{})
counterpart~\citep{shibata:2007}. Observation of an \EM{} counterpart to a
candidate \GW{} event will vastly boost confidence in the \GW{} detection and
will often provide sufficient sky localization to determine
the source's host galaxy and therefore measure the source's redshift. The
\GW{} observation of this event will also provide a luminosity
distance measurement. With both quantities, we can
immediately measure the Hubble constant with unprecedented
accuracy and without systematics dependent on the standard cosmic distance
ladder~\citep{2010ApJ...725..496N}. The most efficient means of obtaining
such joint observations is through the rapid identification and dissemination
of candidate \GW{} events.
